DraftFunctions

### 2021-05-20 R/DraftFunctions.Rmd
Better functions and tests

```{r}
library(Maria)
library(readr)
library(dplyr)
library(tibble)
library(tidyr)
```

@@

# Create a broken dataset
```{r Create a broken dataset}
#in inst/extdata
library(schoolmath)
library(dplyr)

>>>>

```{r}
library(Maria)
library(readr)
library(dplyr)
library(tibble)
library(tidyr)
library(schoolmath)
```

@@

# Create a broken dataset
```{r Create a broken dataset}
#in inst/extdata
